---
title: "SAV Study Item Analysis"
output:
  html_document: default
  html_notebook: default
---
# Load data
```{r}
source('prepare_data.R')
```
# Test data quality
We expect no difference between gender. Participants have to be distributed equally over both conditions sav and pav by gender.
```{r}
table(valid_sessions$gender)
crosstab_gender_assigned_model <- xtabs(~gender+assigned_model, data=valid_sessions); crosstab_gender_assigned_model
chisq.test(crosstab_gender_assigned_model)
```

# Item analysis
```{r}
library(psych)
citation("psych")
```
## Acceptance
### Acceptance of AVs via general attitude
```{r}
items <- c('questionnaire_implicite_general_acceptance_1', 'questionnaire_implicite_general_acceptance_2', 'questionnaire_implicite_general_acceptance_3', 'questionnaire_implicite_general_acceptance_4', 'questionnaire_implicite_general_acceptance_5')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

### Acceptance of AVs via explicit rating over all diemensions
```{r}
items <- c('questionnaire_acceptance_generally', 'questionnaire_acceptance_environmental', 'questionnaire_acceptance_time', 'questionnaire_acceptance_costs', 'questionnaire_acceptance_social')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

## Anticipated Feelings
### Perceptible quantity of potential savings over all dimensions
```{r}
items <- c('questionnaire_apf_quantity_ecology', 'questionnaire_apf_quantity_duration', 'questionnaire_apf_quantity_costs')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

### Anticipated Feelings
```{r}
items <- c('questionnaire_apf_feelings_ecology', 'questionnaire_apf_feelings_duration', 'questionnaire_apf_feelings_costs')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

## Norm and Moral
### Awareness of Consequences
```{r}
items <- c('questionnaire_norm_consequences_1', 'questionnaire_norm_consequences_2')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

### Responsibility
```{r}
items <- c('questionnaire_norm_responsibility_1', 'questionnaire_norm_responsibility_2')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

### Personal Norm
```{r}
items <- c('questionnaire_norm_personality_1', 'questionnaire_norm_personality_2')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

## Implicit assessment
### Ranking
```{r}
valid_sessions_with_sorted_ranking <- subset(valid_sessions, ranking_sorted == TRUE)
nrow(valid_sessions_with_sorted_ranking)

table(valid_sessions_with_sorted_ranking$questionnaire_dimension_ranking_time)
barplot(table(valid_sessions_with_sorted_ranking$questionnaire_dimension_ranking_time), main='Ranking Time')

table(valid_sessions_with_sorted_ranking$questionnaire_dimension_ranking_environment)
barplot(table(valid_sessions_with_sorted_ranking$questionnaire_dimension_ranking_environment), main='Ranking Environment')

table(valid_sessions_with_sorted_ranking$questionnaire_dimension_ranking_costs)
barplot(table(valid_sessions_with_sorted_ranking$questionnaire_dimension_ranking_costs), main='Ranking Costs')

table(valid_sessions_with_sorted_ranking$questionnaire_dimension_ranking_social)
barplot(table(valid_sessions_with_sorted_ranking$questionnaire_dimension_ranking_social), main='Ranking Sozial')
```

### Time
```{r}
items <- c('questionnaire_impicit_time_1', 'questionnaire_impicit_time_2', 'questionnaire_impicit_time_3')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

### Environment
```{r}
items <- c('questionnaire_impicit_environment_1', 'questionnaire_impicit_environment_2', 'questionnaire_impicit_environment_3')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

### Costs
```{r}
items <- c('questionnaire_impicit_costs_1', 'questionnaire_impicit_costs_2', 'questionnaire_impicit_costs_3')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

### Social
```{r}
items <- c('questionnaire_impicit_social_1', 'questionnaire_impicit_social_2', 'questionnaire_impicit_social_3')
alpha(valid_sessions[,items], check.keys=TRUE)
describe(rowMeans(valid_sessions[,items], na.rm = T))
hist(rowMeans(valid_sessions[,items], na.rm = T), main='')
```

## Factor Analysis Contextual Factors
### PAV
```{r}
items <- names(valid_sessions)[grepl( "questionnaire_context_" , names(valid_sessions))]
items <- items[items != 'questionnaire_context_needs_3']
items <- items[items != 'questionnaire_context_needs_4']
items <- items[items != 'questionnaire_context_needs_9']
items <- items[items != 'questionnaire_context_needs_10']
items <- items[items != 'questionnaire_context_concerns_2']
items <- items[items != 'questionnaire_context_concerns_3']
items <- items[items != 'questionnaire_context_concerns_4']

# Determine Number of Factors to Extract
mydata <- valid_sessions.pav[,items]
ev <- eigen(cor(mydata))
ap <- parallel(subject=nrow(mydata),var=ncol(mydata),rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)

res1b <- factanal(mydata, factors=4, rotation="varimax")
print( res1b$loadings, cutoff=0.3 )
```
### SAV
```{r}
items <- names(valid_sessions)[grepl( "questionnaire_context_" , names(valid_sessions))]
# Determine Number of Factors to Extract
mydata <- valid_sessions.sav[,items]
ev <- eigen(cor(mydata))
ap <- parallel(subject=nrow(mydata),var=ncol(mydata),rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)

res1b <- factanal(mydata, factors=7, rotation="varimax")
print( res1b$loadings, cutoff=0.3 )
```
### SAV + PAV 
```{r}
items <- names(valid_sessions)[grepl( "questionnaire_context_" , names(valid_sessions))]
items <- items[items != 'questionnaire_context_needs_3']
items <- items[items != 'questionnaire_context_needs_4']
items <- items[items != 'questionnaire_context_needs_9']
items <- items[items != 'questionnaire_context_needs_10']
items <- items[items != 'questionnaire_context_concerns_2']
items <- items[items != 'questionnaire_context_concerns_3']
items <- items[items != 'questionnaire_context_concerns_4']
# Determine Number of Factors to Extract
mydata <- valid_sessions[,items]
ev <- eigen(cor(mydata))
ap <- parallel(subject=nrow(mydata),var=ncol(mydata),rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)

res1b <- factanal(mydata, factors=4, rotation="varimax")
print( res1b$loadings, cutoff=0.3 )
```
## Innovation
```{r}
tmp <- table(valid_sessions$questionnaire_adoption);tmp[c('innovators','early_adopters','early_majority','late_majority','traditionalist')]
barplot(tmp[c('innovators','early_adopters','early_majority','late_majority','traditionalist')], main='')
```

