---
title: "Stepwise Variable Selection  PAV and SAV"
author: "Markus Graf"
date: "10 8 2017"
output: html_document
---
```{r}
library('corrplot')
library('corrgram')
library('lm.beta')
library('MASS')
source('prepare_data.R')
```
## Definition of available variables
```{r}
catecorial_vars <- c('car_category',
                     'gender',
                     'car_car_owner',
                     'innovation',
                     'assigned_model')

ordinal_vars <- c('urban_vs_rural_areas_2000',
                  'community_size_class',
                  'education',
                  'income')

interval_vars <- c(
  'implicit_time',
  'implicit_costs',
  'implicit_social',
  'implicit_environment',
  'apf_feelings',
  'apf_quantity',
  'norm_consequences',
  'norm_responsibility',
  'norm_personality',
  'age')
```

## Testing for collinearity
### Intercorrelation
```{r}
Hmisc::rcorr(as.matrix(valid_sessions[,c(interval_vars, ordinal_vars, 'explicit_acceptance')]))
corrplot(Hmisc::rcorr(as.matrix(valid_sessions[,c(interval_vars, ordinal_vars, 'explicit_acceptance')]))$r)
```

apf_quantity and apf_feelings is correlating to high so we have to exclude the one that's correlate less with the independend variable.

```{r}
Hmisc::rcorr(as.matrix(valid_sessions[,c('apf_quantity', 'apf_feelings', 'explicit_acceptance')]))
```

So we exclude apf_quantity.

```{r}
interval_vars <- interval_vars[!interval_vars %in% c('apf_quantity')]
```

```{r}
corrgram(valid_sessions[,c(interval_vars, ordinal_vars, 'explicit_acceptance')],order=TRUE, lower.panel=panel.ellipse, upper.panel=panel.pts, text.panel=panel.txt, diag.panel=panel.minmax,cor.method = 'spearman')
```

### Variance inflation factor
```{r}
vif <- bestglm::vifx(valid_sessions[,c(interval_vars)]); vif
```

VIF should be less then 10. So we have to exclude route_duration

```{r}
interval_vars <- interval_vars[!interval_vars %in% c('route_duration')]
vif <- bestglm::vifx(valid_sessions[,c(interval_vars)]); vif
```

```{r}
1/vif
```

Tolerance is greater then 0.2

## Searching for the best general linear model
```{r}
# prepare the dataset and generate the formula
dataset = na.omit(valid_sessions[,c(interval_vars, ordinal_vars, catecorial_vars,'explicit_acceptance')])
left.hand.side  <- 'explicit_acceptance'
predictors <- c(interval_vars, ordinal_vars, catecorial_vars)
right.hand.side <- apply(X = combn(predictors, length(predictors)), MARGIN = 2, paste, collapse = " + ")
model <- paste(left.hand.side, right.hand.side, sep = "  ~  ")
print(model)
# Fit model with all variables included
fit <- glm(as.formula(model),data=dataset)

# Calculate the best model using BIC as creteria
step.bic <- stepAIC(fit, k=log(nrow(dataset)), trace=F, steps = 500000)
summary.lm(step.bic)

# Print Betas
lm.beta(step.bic)

# Inspect the model properties
plot(step.bic)
```


