---
title: "Variable selection"
author: "Markus Graf"
date: "10 8 2017"
output: html_document
---
```{r}
library('bestglm')
library('corrplot')
library('lm.beta')
source('prepare_data.R')
```
## Definition of available variables
```{r}
catecorial_vars <- c('car_category',
                     'gender',
                     'car_car_owner',
                     'innovation')

ordinal_vars <- c('urban_vs_rural_areas_2000',
                  'community_size_class',
                  'education',
                  'income')

interval_vars <- c('implicite_general_acceptance',
                   'impicit_time',
                   'impicit_costs',
                   'impicit_environment',
                   'impicit_social',
                   'apf_feelings',
                   'apf_quantity',
                   'norm_consequences',
                   'norm_responsibility',
                   'norm_personality',
                   'age',
                   'context_positive_antizipation',
                   'context_autonomy',
                   'context_aversion',
                   'driving_enjoyment')
```

## Testing for collinearity
### Intercorrelation
```{r}
Hmisc::rcorr(as.matrix(valid_sessions.pav[,c(interval_vars, ordinal_vars)]))
corrplot(Hmisc::rcorr(as.matrix(valid_sessions.pav[,c(interval_vars, ordinal_vars)]))$r)
```

apf_quantity and apf_feelings is correlating to high so we have to exclude the one that's correlate less with the independend variable.

```{r}
Hmisc::rcorr(as.matrix(valid_sessions[,c('apf_quantity', 'apf_feelings', 'explicit_acceptance')]))
```

So we exclude apf_quantity.

```{r}
interval_vars <- interval_vars[!interval_vars %in% c('apf_quantity')]
```


### Variance inflation factor
```{r}
vif.pav <- bestglm::vifx(valid_sessions.pav[,c(interval_vars)]); vif.pav
```

VIF should be less then 10.

```{r}
1/vif.pav
```

Tolerance is greater then 0.2

## Searching for the best general linear model
```{r}
resbestglm.pav <- bestglm(na.omit(valid_sessions.pav[,c(interval_vars, ordinal_vars, catecorial_vars, 'explicit_acceptance')]))
summary(resbestglm.pav$BestModel)
lm.beta(resbestglm.pav$BestModel)
save(resbestglm.pav, file = 'resbestglm.pav.Rdata')
```

