---
title: "Variable selection"
author: "Markus Graf"
date: "10 8 2017"
output: html_document
---
```{r}
library('bestglm')
library('corrplot')
library('lm.beta')
source('prepare_data.R')
```
## Definition of available variables
```{r}
catecorial_vars <- c('car_category',
                     'gender',
                     'car_car_owner',
                     'innovation',
                     'assigned_model')

ordinal_vars <- c('urban_vs_rural_areas_2000',
                  'community_size_class',
                  'education',
                  'income')

interval_vars <- c('implicite_general_acceptance',
                   'impicit_time',
                   'impicit_costs',
                   'impicit_environment',
                   'impicit_social',
                   'apf_feelings',
                   'apf_quantity',
                   'norm_consequences',
                   'norm_responsibility',
                   'norm_personality',
                   'age')
```

## Testing for collinearity
### Intercorrelation
```{r}
Hmisc::rcorr(as.matrix(valid_sessions[,c(interval_vars, ordinal_vars, 'explicit_acceptance')]))
corrplot(Hmisc::rcorr(as.matrix(valid_sessions.pav[,c(interval_vars, ordinal_vars, 'explicit_acceptance')]))$r)
```

apf_quantity and apf_feelings is correlating to high so we have to exclude the one that's correlate less with the independend variable.

```{r}
Hmisc::rcorr(as.matrix(valid_sessions[,c('apf_quantity', 'apf_feelings', 'explicit_acceptance')]))
```

So we exclude apf_quantity.

```{r}
interval_vars <- interval_vars[!interval_vars %in% c('apf_quantity')]
```

```{r}
corrgram(valid_sessions[,c(interval_vars, ordinal_vars, 'explicit_acceptance')],order=TRUE, lower.panel=panel.ellipse, upper.panel=panel.pts, text.panel=panel.txt, diag.panel=panel.minmax,cor.method = 'spearman')
```
### Variance inflation factor
```{r}
vif <- bestglm::vifx(valid_sessions[,c(interval_vars)]); vif
```

VIF should be less then 10.

```{r}
1/vif
```

Tolerance is greater then 0.2

## Searching for the best general linear model
```{r}
resbestglm <- bestglm(na.omit(valid_sessions[,c(interval_vars, ordinal_vars, catecorial_vars, 'explicit_acceptance')]))
print.bestglm(resbestglm$BestModel)
lm.beta(resbestglm$BestModel)
save(resbestglm, file = 'resbestglm.Rdata')
```

