---
title: "Variable selection"
author: "Markus Graf"
date: "10 8 2017"
output: html_document
---
```{r}
library('parallel')
library('corrplot')
library('lm.beta')
source('prepare_data.R')
```
## Definition of available variables
```{r}
catecorial_vars <- c('car_category',
                     'gender',
                     'car_car_owner',
                     'innovation')

ordinal_vars <- c('urban_vs_rural_areas_2000',
                  'community_size_class',
                  'education',
                  'income')

interval_vars <- c('implicite_general_acceptance',
                   'impicit_time',
                   'impicit_costs',
                   'impicit_environment',
                   'impicit_social',
                   'apf_feelings',
                   'apf_quantity',
                   'norm_consequences',
                   'norm_responsibility',
                   'norm_personality',
                   'age',
                   'context_positive_antizipation',
                   'context_autonomy',
                   'context_aversion',
                   'driving_enjoyment')
```

## Testing for collinearity
### Intercorrelation
```{r}
Hmisc::rcorr(as.matrix(valid_sessions.pav[,c(interval_vars, ordinal_vars)]))
corrplot(Hmisc::rcorr(as.matrix(valid_sessions.pav[,c(interval_vars, ordinal_vars)]))$r)
```

apf_quantity and apf_feelings is correlating to high so we have to exclude the one that's correlate less with the independend variable.

```{r}
Hmisc::rcorr(as.matrix(valid_sessions[,c('apf_quantity', 'apf_feelings', 'explicit_acceptance')]))
```

So we exclude apf_quantity.

```{r}
interval_vars <- interval_vars[!interval_vars %in% c('apf_quantity')]
```


### Variance inflation factor
```{r}
vif.pav <- bestglm::vifx(valid_sessions.pav[,c(interval_vars)]); vif.pav
```

VIF should be less then 10. 

```{r}
1/vif.pav
```

Tolerance is greater then 0.2

## Searching for the best general linear model
```{r}
predictors = c(interval_vars, ordinal_vars, catecorial_vars)
outcome = c('explicit_acceptance')
dataset <- valid_sessions.pav

## Create list of models
list.of.models <- mclapply(seq_along((predictors)), function(n) {
  
  left.hand.side  <- outcome
  right.hand.side <- apply(X = combn(predictors, n), MARGIN = 2, paste, collapse = " + ")
  
  paste(left.hand.side, right.hand.side, sep = "  ~  ")
}, mc.cores=(parallel::detectCores() -1), mc.allow.recursive=T)

## Convert to a vector
vector.of.models <- unlist(list.of.models)
start.time <- Sys.time()

## Fit glm to all models
list.of.fits <- mclapply(vector.of.models, function(x) {
  formula    <- as.formula(x)
  fit        <- glm(formula, data = dataset)
  result.BIC <- extractAIC(fit, k = log(nrow(dataset)))
  
  data.frame(num.predictors = result.BIC[1],
             BIC            = result.BIC[2],
             model          = x)
}, mc.cores=(parallel::detectCores()-1), mc.allow.recursive=T)
end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken

## Collapse to a data frame
list.of.fits.sorted <- list.of.fits[order(sapply(list.of.fits,'[[',2))]
myBestglm.pav <- glm(as.character(list.of.fits.sorted[[1]][3]$model), data=dataset)
myBestglm.pav
summary(myBestglm.pav)
save.image(file='CrystalBallPavDiy.RData')
```

